On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-01 tt_theorem.tex
12/1 before dinner

\begin{proof}[lemma \ref{TTT_entrance_Tab}]
See Fig.\ref{TTT_tunnel_direction}.
$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section type of $S$ or $O$.
Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
We now prove that $w[i]$ must form a bond.

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$. If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $t_a \in S[h+1..i]$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

@@

\subsubsection{Case of $S[h-1..h+1] = bbt$}
Let us consider number of consumed bindings by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).

\begin{itemize}
\item{$w[h-1]$ consumes one binding}\\
  In this situation, $w[h-1]$ supplies one active binding whereas $w[h+1]$ consumes this binding. In addition, $w[h]$ has to bound to one of $n_1, n_2, n_3$.
  Thus, in this cases consume some binding capabilities.

\item{$w[h-1]$ consumes two bindings}\\
  In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
\end{itemize}

>>>>

\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
See Fig.\ref{TTT_tunnel_direction}.
$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
We now prove that $w[i]$ must form a bond.

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$. If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

\subsubsection{Case of $S[h-1..h+1] = bbt$}
See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
In addition, $w[h]$ has to bound.
Thus, in this cases, binding capability decreases by 1.
If $w[h-1]$ forms two bonds, then it does not leave any bond.
In addition, $w[h]$ has to be bound.
Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.

@@
